# Números naturales {#intro}

```{definition, name="conjunto inductivo"}
Un conjunto $M$ es inductivo si verifica las siguentes condiciones

1. $0\in M$
1. si $x\in M$ entonces $x+1\in M$
```


```{theorem, www}
Todo conjunto  indcutivo de numeros reales contiene  los numeros 1, 2, 3, $\ldots$
```

```{proof, troll}
En efecto $0\in M$, $0+1\in M$
```



```{theorem, w1, name="Principio de inducción matemática"}
Todo conjunto  indcutivo de numeros reales contiene  los numeros 1, 2, 3, $\ldots$
```

You can label chapter and section titles using after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in and environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the  prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
