# Introduction {#intro}
```{theorem, www, name="russ"}
Dada el espacio $R$ y $r\in R$ se tiene que $\mathcal{R}(r)=\lim_{t\to\infty}g(y)_r$
```

```{proof, troll}
En efecto haciendo el intercambio de variables se tiene que $\sum_{i=1}^{\infty}r_i$ 
$$\vec{r}=\abs{\frac{\vec{\int_1^2r}}{\left|r_1^2\right|}}\norm{\int_1^2e}$$
por lo tanto se cumple.
```

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
